### 2019-02-06 sections/semantics.tex
scale figures for new format
remove mathpartir and use custom rule macros

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth,page=5]{figures/drawings-crop.pdf}
  \caption{
    Semantic functions defined in this report and their relation.
  }
  \label{fig:semantic-functions}
\end{figure}

@@

% \begin{figure}[h]
%
%   \begin{mathpar}
%     \userule{E-Edit} \quad
%     \userule{E-Enter} \quad
%     \userule{E-Update} \\
%     \userule{E-Then} \quad
%     \userule{E-Next} \\
%     \userule{E-And} \quad
%     \userule{E-Or} \\
%     \userule{E-Xor} \quad
%     \userule{E-Appoint} \quad
%     \userule{E-Fail}
%   \end{mathpar}
%
%   \caption{Evaluation semantics for pretasks} \label{}
% \end{figure}

@@

  \boxed{\RelationN}
  \begin{mathpar}
    \userule{N-Done} \\
    \userule{N-Repeat}
  \end{mathpar}
  \caption{Normalisation semantics} \label{fig:normalisation-semantics}

@@

  \begin{mathpar}
    \boxed{\RelationS}
  \end{mathpar}

  \paragraph{Step}
  \begin{mathpar}
    \userule{S-ThenStay} \\
    \userule{S-ThenFail} \\
    \userule{S-ThenCont}
  \end{mathpar}

  \paragraph{Choose}
  \begin{mathpar}
    \userule{S-OrLeft} \\
    \userule{S-OrRight} \\
    \userule{S-OrNone}
  \end{mathpar}

  \paragraph{Ready}
  \begin{mathpar}
    \userule{S-Edit} \quad \userule{S-Fill} \qquad \userule{S-Update} \\
    \userule{S-Fail} \quad \userule{S-Xor}
  \end{mathpar}

  \paragraph{Congruence}
  \begin{mathpar}
    \userule{S-Next} \quad
    \userule{S-And} \\
    %\userule{S-Appoint}
    % \userule{S-Eval}
  \end{mathpar}

@@

\begin{figure}[h]
  \small
  \begin{mathpar}
    \boxed{\RelationI} \\
    \userule{I-Handle}
  \end{mathpar}
  \caption{Interaction semantics} \label{fig:interaction-semantics}
\end{figure}

@@

  \begin{mathpar}
    \boxed{\RelationH}
  \end{mathpar}

  \paragraph{Editing}
  \begin{mathpar}
    \userule{H-Change} \quad
    \userule{H-Empty} \\
    \userule{H-Fill} \quad
    \userule{H-Update}
  \end{mathpar}

  \paragraph{Continuing}
  \begin{mathpar}
    \userule{H-Next} \\
    \userule{H-PickLeft} \quad
    \userule{H-PickRight}
  \end{mathpar}

  \paragraph{Passing}
  \begin{mathpar}
    \userule{H-PassThen} \quad \userule{H-PassNext} \\
    \userule{H-FirstAnd} \quad \userule{H-SecondAnd} \\
    \userule{H-FirstOr}  \quad \userule{H-SecondOr}\\
  %  \userule{H-Appoint}
  \end{mathpar}

@@

\smallcaps{H-Change},
\smallcaps{H-Empty},
\smallcaps{H-Fill},
\smallcaps{H-Update}:
Input events $v$ and $\Empty$ are used to change the value of editors and empty them.
Editors only accept values of the correct type.

\smallcaps{H-Next}:
The $\Continue$(ontinue) action triggers an external step.
As with internal stepping, this is only possible if the left side has a value and the continuation is not failing.

\smallcaps{H-PickLeft},
\smallcaps{H-PickRight}:
$\Left$ and $\Right$ are used to pick the left or right option of an external choice.

\smallcaps{H-PassThen},
\smallcaps{H-PassNext}:
The step combinators pass all events other than $\Continue$ to the left side.

\smallcaps{H-FirstAnd},
\smallcaps{H-SecondAnd},
\smallcaps{H-FirstOr},
\smallcaps{H-SecondOr}:
Inputs $\First$(irst) and $\Second$(econd) are used to direct inputs to the correct branch of parallel combinations.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\columnwidth,page=5]{figures/drawings-crop.pdf}
  \caption{
    Semantic functions defined in this report and their relation.
  }
  \label{fig:semantic-functions}
\end{figure}

@@

% \begin{figure}[h]
%
%   \begin{gather*}
%     \userule{E-Edit} \Quad
%     \userule{E-Enter} \Quad
%     \userule{E-Update} \Break
%     \userule{E-Then} \Quad
%     \userule{E-Next} \Break
%     \userule{E-And} \Quad
%     \userule{E-Or} \Break
%     \userule{E-Xor} \Quad
%     \userule{E-Appoint} \Quad
%     \userule{E-Fail}
%   \end{gather*}
%
%   \caption{Evaluation semantics for pretasks} \label{}
% \end{figure}

@@

  \boxed{\RelationN}
  \begin{gather*}
    \userule{N-Done} \Break
    \userule{N-Repeat}
  \end{gather*}
  \caption{Normalisation semantics} \label{fig:normalisation-semantics}

@@

  \begin{gather*}
    \boxed{\RelationS}
  \end{gather*}

  \paragraph{Step}
  \begin{align*}
    \userule{S-ThenStay} \Quad
    & \userule{S-ThenFail} \Break
    & \userule{S-ThenCont}
  \end{align*}

  \paragraph{Choose}
  \begin{align*}
    \userule{S-OrLeft} \Quad
    & \userule{S-OrRight} \Break
    & \userule{S-OrNone}
  \end{align*}

  \paragraph{Ready}
  \begin{gather*}
    \userule{S-Edit} \Quad \userule{S-Fill} \Quad \userule{S-Update} \Quad
    \userule{S-Fail} \Quad \userule{S-Xor}
  \end{gather*}

  \paragraph{Congruence}
  \begin{gather*}
    \userule{S-Next} \Quad
    \userule{S-And}
    %\userule{S-Appoint}
    % \userule{S-Eval}
  \end{gather*}

@@

\begin{figure}[h]
  \small
  \begin{gather*}
    \boxed{\RelationI} \Break
    \userule{I-Handle}
  \end{gather*}
  \caption{Interaction semantics} \label{fig:interaction-semantics}
\end{figure}

@@

  \begin{gather*}
    \boxed{\RelationH}
  \end{gather*}

  \paragraph{Editing}
  \begin{gather*}
    \userule{H-Change} \Quad
    \userule{H-Empty} \Break
    \userule{H-Fill} \Quad
    \userule{H-Update}
  \end{gather*}

  \paragraph{Continuing}
  \begin{gather*}
    \userule{H-Next} \Break
    \userule{H-PickLeft} \Quad
    \userule{H-PickRight}
  \end{gather*}

  \paragraph{Passing}
  \begin{gather*}
    \userule{H-PassThen} \Quad \userule{H-FirstAnd} \Quad \userule{H-FirstOr} \Break
    \userule{H-PassNext} \Quad \userule{H-SecondAnd} \Quad \userule{H-SecondOr}
  %  \userule{H-Appoint}
  \end{gather*}

@@

\refrule{H-Change},
\refrule{H-Empty},
\refrule{H-Fill},
\refrule{H-Update}:
Input events $v$ and $\Empty$ are used to change the value of editors and empty them.
Editors only accept values of the correct type.

\refrule{H-Next}:
The $\Continue$(ontinue) action triggers an external step.
As with internal stepping, this is only possible if the left side has a value and the continuation is not failing.

\refrule{H-PickLeft},
\refrule{H-PickRight}:
$\Left$ and $\Right$ are used to pick the left or right option of an external choice.

\refrule{H-PassThen},
\refrule{H-PassNext}:
The step combinators pass all events other than $\Continue$ to the left side.

\refrule{H-FirstAnd},
\refrule{H-SecondAnd},
\refrule{H-FirstOr},
\refrule{H-SecondOr}:
Inputs $\First$(irst) and $\Second$(econd) are used to direct inputs to the correct branch of parallel combinations.
